### 2024-07-25 paper.tex
fix definition of c's, and write proof of what a,b look like for general X

\subsection{In the case of general \(X\)}
In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
In the general case, it is not clear that such a thing should be true.
And indeed it is not.
However, we will see that we can change basis of \(\mathbb{C}^m\) so that a similar thing is true.
\par Let \(c_{i',j'}^i \in \mathbb{C}\) be some arbitrary coefficients.
Given our Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\), we can define a new Jordan basis \(e_{ij}'\) of \(\mathbb{C}^m\) by 
\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
Then we define
\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
Let us calculate the new value \(a'\) of \(a\) in this new basis.
That is, we want the values \(a_{ij}'\) that satisfy \(Ae_{ij}' = e_{i, j - 1}' + a_{ij}' f_1\).
Looking at the definition of \(e_{ij}'\) above, we see that
\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
\par Now, for each \(i\), choose the coefficients \(c_{i',j'}^i\) to maximize the value \(\max\{j : (a_{i,1}', ..., a_{i, j}') = 0\}\).
In other words, we choose \(c_{i'j'}^i\) to zero out the largest possible prefix of \((a_{i, 1}, ..., a_{i, \lambda_i})\).
\begin{lemma}
    The condition of \cref{ab_nilp} on \(a\) and \(b\) holds iff there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
    \begin{itemize}
        \item \(\lambda_i = p_i + q_i + r_i\)
        \item \((a_{i,1}, ..., a_{i,\lambda_i}) = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
        \item \((b_{i, 1}, ..., b_{i, \lambda_i}) = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
        \item If \(r_i \neq 0\), then \(a_1 \neq 0\)
        \item If \(p_i \neq 0\), then \(b_{p_i} \neq 0\)
    \end{itemize}
\end{lemma}
\begin{proof}

>>>>

\subsection{In the case of general \(X\)}
In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
In the general case, it is not clear that such a thing should be true.
And indeed it is not.
However, we will see that we can change basis of \(\mathbb{C}^m\) so that a similar thing is true.
\par Let \(c_{i',j'}^i \in \mathbb{C}\) be some arbitrary coefficients.
Given our Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\), we can define a new Jordan basis \(e_{ij}'\) of \(\mathbb{C}^m\) by 
\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
Then we define
\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
Let us calculate the new value \(a'\) of \(a\) in this new basis.
That is, we want the values \(a_{ij}'\) that satisfy \(Ae_{ij}' = e_{i, j - 1}' + a_{ij}' f_1\).
Looking at the definition of \(e_{ij}'\) above, we see that
\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
\par Now, for each \(i\), choose the coefficients \(c_{i',j'}^i\) to maximize the value \(\max\{j : (a_{i,1}', ..., a_{i, j}') = 0\}\).
In other words, we choose \(c_{i'j'}^i\) to zero out the largest possible prefix of \((a_{i, 1}, ..., a_{i, \lambda_i})\).
\begin{lemma}
    If the condition of \cref{ab_nilp} on \(a'\) and \(b'\) holds, then there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
    \begin{itemize}
        \item \(\lambda_i = p_i + q_i + r_i\)
        \item \((a_{i,1}', ..., a_{i,\lambda_i}') = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
        \item \((b_{i, 1}', ..., b_{i, \lambda_i}') = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
        \item If \(r_i \neq 0\), then \(\alpha_{i,1} \neq 0\)
        \item If \(p_i \neq 0\), then \(\beta_{i, p_i} \neq 0\)
    \end{itemize}
\end{lemma}
\begin{proof}
    We begin with the first row of \(\lambda\), namely \(i = 1\).
    Let \(k = \min\{j : a'_{1,j} \neq 0\}\) and \(l = \max\{j : b'_{1, j} \neq 0\}\).
    I just need to show that \(l < k\).
    Suppose not.
    Then \((l - k)\) is nonnegative, and by \cref{ab_nilp} we have 
    \[0 = \sum_{ij} b_{ij}' a_{j - (l - k)}' = b_{1,l}' a_{1,k}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{ij} a'_{j - (l - k)}.\]
    This suggests defining 
    \[e_{1,\lambda_1}'' = b_{1, l}'e_{1, \lambda_1}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i',j' - (\lambda_1 - l)} e'_{i'j'}.\]
    Then for \(j \leq k\),
    \[a_{1,j}'' = b'_{1, l} a'_{1, j} + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \]
    \[\sum_{i', j'} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \sum_{i', j'} b'_{i', j'} a'_{i', (j' + (\lambda_1 - l)) - (\lambda_1 - j)} = \sum_{i',j'} b'_{i',j'} a'_{i', j' - (l - j)}.\]
    This last thing is zero by \cref{ab_nilp}, using that \(l - j \geq 0\).
    But this contradicts the definition of the \(c_{i'j'}^1\), because we made it so that \((a''_{1, 1}, ..., a''_{1, k}) = 0\).
